
@ARTICLE{Dai_TSP_2009,  
author={Dai, Xuewu and Gao, Zhiwei and Breikin, Tim and Wang, Hong},  journal={IEEE Transactions on Signal Processing},   title={Zero Assignment for Robust  ${H}_{2}/{H}_{\infty}$ Fault Detection Filter Design},   year={2009},  volume={57},  number={4},  pages={1363-1372}}

@article{Patel_TAC_1986,
  author={Patel, R.},
  journal={IEEE Transactions on Automatic Control}, 
  title={On Blocking Zeros in Linear Multivariable Systems}, 
  year={1986},
  volume={31},
  number={3},
  pages={239-241}}

@inproceedings{Schrader_CDC_1989,
  author={Schrader, C.B. and Sain, M.K.},
  booktitle={Proceedings of the 27th IEEE Conference on Decision and Control}, 
  title={Research on system zeros: a survey}, 
  year={1988},
  volume={},
  number={},
  pages={890-901}}

@article{Wu_2006_TCASI,
  author={Wu, Ai-Guo and Duan, Guang-Ren},
  journal={IEEE Transactions on Circuits and Systems I: Regular Papers}, 
  title={Design of Generalized {PI} Observers for Descriptor Linear Systems}, 
  year={2006},
  volume={53},
  number={12},
  pages={2828-2837}}

@book{Bhatia_book,
  title={Matrix analysis},
  author={ Bhatia, R. },
  publisher={Matrix Analysis},
  year={1996}}

@article{White_2023_TCST,
  title={Mixed ${H}_{2} / {H}_{\infty}$ Observer-Based LPV Control of a Hydraulic Engine Cam Phasing Actuator},
  author={ White, A.  and  Zhen, R.  and  Zhu, G.  and  Choi, J. },
  journal={IEEE Transactions on Control Systems Technology},
  volume={21},
  number={1},
  pages={229-238},
  year={2013}}

@INPROCEEDINGS{Canale_2013_ECC,
  author={Canale, Massimo and Brunet, Simone Casale},
  booktitle={2013 European Control Conference (ECC)}, 
  title={A Lego Mindstorms NXT experiment for Model Predictive Control education}, 
  year={2013},
  volume={},
  number={},
  pages={2549-2554}}

@ARTICLE{Kim_2019_TCAS2,
  author={Kim, Seok-Kyoon and Ahn, Choon Ki},
  journal={IEEE Transactions on Circuits and Systems II: Express Briefs}, 
  title={Self-Tuning Position-Tracking Controller for Two-Wheeled Mobile Balancing Robots}, 
  year={2019},
  volume={66},
  number={6},
  pages={1008-1012}}

@ARTICLE{Hu_2023_TIE,
  author={Dai, Xuewu and Hu, Yuxiang and Cui, Dongliang and Chai, Tianyou},
  journal={IEEE Trans. Ind. Electron.}, 
  title={A disturbance decoupling generalized proportional-integral observer design for robust sensor fault detection}, 
  year={Jun. 2023},
  volume={70},
  number={6},
  pages={6326-6336}}

@article{Hu_2018_CEP,
author = {He, Zhangming and Shardt, Yuri A.W. and Wang, Dayi and Hou, Bowen and Zhou, Haiyin and Wang, Jiongqi },
title = {An incipient fault detection approach via detrending and denoising},
journal = {Control Eng. Practice},
volume = {74},
pages = {1-12},
year = {May 2018},
issn = {0967-0661}}

@ARTICLE{Hu_2024_TII,
  author={Hu, Yuxiang and Dai, Xuewu and Cui, Dongliang and Chai, Tianyou},
  journal={IEEE Trans. Ind. Inform.}, 
  title={Detection and identification of cyberattacks and physical faults in multi-agent systems: A distributed disturbance decoupling observer}, 
  year={Feb. 2024},
  volume={20},
  number={2},
  pages={2991-3001}}

@ARTICLE{Chen_2022_TCYB,
  author={Chen, Zhiwen and Xu, Jiamin and Peng, Tao and Yang, Chunhua},
  journal={IEEE Trans. Cybern.}, 
  title={Graph convolutional network-based method for fault diagnosis using a hybrid of measurement and prior knowledge}, 
  year={Sept. 2022},
  volume={52},
  number={9},
  pages={9157-9169}}


@ARTICLE{Zhong_2023_IATM,
  author={Zhong, Kai and Han, Bing and Han, Min and Chen, Hongtian},
  journal={IEEE/ASME Trans. Mechatron.}, 
  title={Hierarchical graph convolutional networks with latent structure learning for mechanical fault diagnosis}, 
  year={Dec. 2023},
  volume={28},
  number={6},
  pages={3076-3086}}

@ARTICLE{Jiang_2020_CVPR,
  author={Jiang, Bo and Zhang, Ziyan and Lin, Doudou and Tang, Jin and Luo, Bin},
  journal={Proc. IEEE Comput. Soc. Conf. Comput. Vis. Pattern Recognit.}, 
  title={Semi-supervised learning with graph learning-convolutional networks}, 
  year={Jan. 2020},
  volume={},
  number={},
  pages={11305-11312}}


@ARTICLE{Zhao_2020_TITS,
  author={Zhao, Ling and Song, Yujiao and Zhang, Chao and Liu, Yu and Wang, Pu and Lin, Tao and Deng, Min and Li, Haifeng},
  journal={IEEE Trans. Intell. Transp. Syst.}, 
  title={T-{GCN}: A temporal graph convolutional network for traffic prediction}, 
  year={2020},
  volume={21},
  number={9},
  pages={3848-3858}}



@ARTICLE{Song_2024_TII,
  author={Song, Bing and Zheng, Chengfeng and Jin, Yuting and Shi, Hongbo and Tao, Yang and Tan, Shuai},
  journal={IEEE Trans. Ind. Inform.}, 
  title={A fault-targeted gated recurrent unit-canonical correlation analysis method for incipient fault detection}, 
  year={Jun. 2024},
  volume={20},
  number={6},
  pages={8739-8748}}


%%%%%


%%%%%

@ARTICLE{Li_2023_TIM,
  author={Li, Qiyue and Luo, Huan and Cheng, Hong and Deng, Yuxing and Sun, Wei and Li, Weitao and Liu, Zhi},
  journal={IEEE Trans. Instrum. Meas.}, 
  title={Incipient fault detection in power distribution system: A time–frequency embedded deep-learning-based approach}, 
  year={Feb. 2023},
  volume={72},
  number={},
  pages={1-14}}


@ARTICLE{Chen_2019_TIE,
  author={Chen, Hongtian and Jiang, Bin and Chen, Wen and Yi, Hui},
  journal={IEEE Trans. Ind. Electron.}, 
  title={Data-driven detection and diagnosis of incipient faults in electrical drives of high-speed trains}, 
  year={Jun. 2019},
  volume={66},
  number={6},
  pages={4716-4725}}

@ARTICLE{Zhang_2021_ICAS,
  author={Zhang, Dan and Feng, Gang and Shi, Yang and Srinivasan, Dipti},
  journal={IEEE/CAA J. Autom. Sinica}, 
  title={Physical safety and cyber security analysis of multi-agent systems: A survey of recent advances}, 
  year={Feb. 2021},
  volume={8},
  number={2},
  pages={319-333}}

@ARTICLE{Chen_2024_TITS,
  author={Chen, Hongtian and Luo, Hao and Huang, Biao and Jiang, Bin and Kaynak, Okyay},
  journal={IEEE Trans. Neural Netw. Learn. Syst.}, 
  title={Transfer learning-motivated intelligent fault diagnosis designs: A survey, insights, and perspectives}, 
  year={Mar. 2024},
  volume={35},
  number={3},
  pages={2969-2983}}


@ARTICLE{Zhong_2020_TAC,
  author={Zhong, Maiying and Ding, Steven X and Zhou, Donghua and He, Xiao},
  journal={IEEE Trans. Autom. Control}, 
  title={An ${H}_{i}/{H}_{\infty}$ optimization approach to event-triggered fault detection for linear discrete time systems}, 
  year={Jul. 2020},
  volume={65},
  number={10},
  pages={4464-4471}}


@ARTICLE{Jin_2024_TCYB,
  author={Jin, Hailang and Zuo, Zhiqiang and Wang, Yijing and Cui, Lei and Gao, Zhiwei},
  journal={IEEE Trans. Cybern.}, 
  title={Event-triggered interval observer fault detection and isolation for multiagent systems}, 
  year={early access, Jan. 2024, doi: 10.1109/TCYB.2023.3344775.},
  volume={},
  number={},
  pages={}}


@ARTICLE{Han_2022_SMC,
  author={Han, Jian and Liu, Xiuhua and Wei, Xinjiang and Sun, Shaoxin},
  journal={IEEE Trans. Syst. Man Cybern. Syst.}, 
  title={A dynamic proportional-integral observer-based nonlinear fault-tolerant controller design for nonlinear system with partially unknown dynamic}, 
  year={Aug. 2022},
  volume={52},
  number={8},
  pages={5092-5104}}


@ARTICLE{Yang_2023_TTE,
  author={Yang, Ge and Marepalli, Lalit Kishore and Herrera, Luis and Yao, Xiu},
  journal={IEEE Trans. Transp. Electrif.}, 
  title={Series DC arc fault detection in DC microgrids based on distributed unknown input observers}, 
  year={early access, Sep. 2023, doi: 10.1109/TTE.2023.3318430.},
  volume={},
  number={},
  pages={}}


@ARTICLE{Xu_2024_TIM,
  author={Xu, Shuiqing and Chen, Xinyang and Yang, Wei and Liu, Feng and Chai, Yi},
  journal={IEEE Trans. Instrum. Meas.}, 
  title={Current sensor incipient fault diagnosis in PMSM drive systems using novel interval sliding mode observer}, 
  year={Art no. 3508211, 2024},
  volume={73},
  number={},
  pages={1-11}}

@ARTICLE{Jiao_2024_TR,
  author={Jiao, Zhiyuan and Chen, Xiyuan and Gao, Ning},
  journal={IEEE Trans. Reliab.}, 
  title={A novel fault detection framework-based extend kalman filter for fault-tolerant navigation system}, 
  year={early access, Jun. 2024, doi: 10.1109/TR.2024.3405026.},
  volume={},
  number={},
  pages={}}


@ARTICLE{Wang_2024_TIA,
  author={Wang, Yunchong and Li, Peiyi and Shen, Jian-Xin and Jiang, Chenxin and Huang, Xiaoyan and Long, Tan},
  journal={IEEE Trans. Ind. Appl.}, 
  title={Adaptive periodic disturbance observer based on fuzzy logic compensation for speed fluctuation suppression of PMSM under periodic loads}, 
  year={early access, May 2024, doi: 10.1109/TIA.2024.3395573.},
  volume={},
  number={},
  pages={}}


@ARTICLE{Li_2024_TII,
  author={Li, Biao and Yang, Ying},
  journal={IEEE Trans. Ind. Inform.}, 
  title={Data-driven optimal distributed fault detection based on subspace identification for large-scale interconnected systems}, 
  year={Feb. 2024},
  volume={20},
  number={2},
  pages={2497-2507}}


@ARTICLE{Wang_2024_TSG,
  author={Wang, Zhiwei and Jiang, Wei and Xu, Junjun and Xu, Zhiqi and Zhou, Aihua and Xu, Min},
  journal={IEEE Trans. Smart Grid}, 
  title={Grid2Vec: learning node representations of digital power systems for anomaly detection}, 
  year={early access, Mar. 2024, doi: 10.1109/TSG.2024.3377223.},
  volume={},
  number={},
  pages={}}


  %%%%%

@ARTICLE{Qi_2023_TITS,
  author={Qi, Xiaoyu and Mei, Gang and Tu, Jingzhi and Xi, Ning and Piccialli, Francesco},
  journal={IEEE Trans. Intell. Transp. Syst.}, 
  title={A deep learning approach for long-term traffic flow prediction with multifactor fusion using spatiotemporal graph convolutional network}, 
  year={2023},
  volume={24},
  number={8},
  pages={8687-8700}}


@ARTICLE{Wang_2024_TII,
  author={Wang, Lei and He, Yigang and Zhou, Yazhong and Li, Lie and Wang, Jing and Zhao, Yingying and Du, Bolun},
  journal={IEEE Trans. Ind. Inform.}, 
  title={A novel approach to wind turbine blade Icing detection with limited sensor data via spatiotemporal attention siamese network}, 
  year={Jun. 2024},
  volume={20},
  number={6},
  pages={8993-9005}}

  %%%%%%%%%%%%%%%%%%

@ARTICLE{Ma_2024_TCAS1,
  author={Ma, Haoran and Zhao, Zhengen and Li, Zhuyuan and Yang, Ying},
  journal={IEEE Trans. Circuits Syst. I, Reg. Papers}, 
  title={Data-driven passivity analysis and fault detection using reinforcement learning}, 
  year={early access, Jul. 2024, doi: 10.1109/TCSI.2024.3417257}}

@ARTICLE{Yu_2024_TCAS1,
  author={Ma, Yufei and Qiu, Yikan and Zhao, Wentao and Li, Guoxiang and Wu, Meng and Jia, Tianyu and Ye, Le and Huang, Ru},
  journal={IEEE Trans. Circuits Syst. I, Reg. Papers}, 
  title={DCIM-GCN: Digital computing-in-memory accelerator for graph convolutional network}, 
  year={Apr. 2024},
  volume={71},
  number={6},
  pages={2735-2748}}


@ARTICLE{Jia_2024_TASE,
  author={Jia, Zhian and Cui, Dongliang and Dai, Xuewu and Liu, Zhi-Wei and Liu, Shuxin and Chai, Tianyou},
  journal={IEEE Trans. Autom. Sci. Eng.}, 
  title={Low overhead minimum variance time synchronization for time-sensitive wireless sensor networks}, 
  year={early access, Jul. 2024, doi: 10.1109/TASE.2024.3419142}}

@ARTICLE{Gao_2015_TIE_2,
 author={Gao, Zhiwei and Cecati, Carlo and Ding, Steven X.},
  journal={IEEE Trans. Ind. Electron.}, 
  title={A survey of fault diagnosis and fault-tolerant techniques--{P}art {II}: Fault diagnosis with knowledge-based and hybrid/active approaches}, 
  year={Jun. 2015},
  volume={62},
  number={6},
  pages={3768-3774}}


@ARTICLE{Pei_2024_TNSE,
  author={Pei, Xinjun and Deng, Xiaoheng and Xiong, Neal N. and Mumtaz, Shahid and Wu, Jie},
  journal={IEEE Trans. Netw. Sci. Eng.}, 
  title={Complex graph analysis and representation learning: Problems, techniques, and applications}, 
  year={Sept. 2024},
  volume={11},
  number={5},
  pages={4990-5007}}

@ARTICLE{Gao_2015_TIE1,
  author={Gao, Zhiwei and Cecati, Carlo and Ding, Steven X.},
  journal={IEEE Trans. Ind. Electron.}, 
  title={A survey of fault diagnosis and fault-tolerant techniques--{P}art {I}: Fault diagnosis with model-based and signal-based approaches}, 
  year={Jun. 2015},
  volume={62},
  number={6},
  pages={3757-3767}}


@ARTICLE{Zhong_2020_TAC1,
  author={Zhong, Maiying and Ding, Steven X and Zhou, Donghua and He, Xiao},
  journal={IEEE Trans. Autom. Control}, 
  title={An ${H}_{i}/{H}_{\infty }$ optimization approach to event-triggered fault detection for linear discrete time systems}, 
  year={Oct. 2020},
  volume={65},
  number={10},
  pages={4464-4471}}

@ARTICLE{10034781,
  author={Duan, Zhaoxia and Feng, Yuchun and Ahn, Choon Ki and Xiang, Zhengrong},
  journal={IEEE Trans. Circuits Syst. II Exp. Briefs}, 
  title={Mixed ${L}_1/{L}_{-}$ fault detection observer for continuous 2-D positive systems}, 
  year={Jul. 2023},
  volume={70},
  number={7},
  pages={2485-2489}}



@ARTICLE{Zhang_2024_TETCI,
  author={Zhang, Kesheng and Yu, Wen and Chai, Tianyou},
  journal={IEEE Trans. Emerg. Top. Comput. Intell.}, 
  title={Dual-scale attributed graph transformer for extracting spatial-temporal features with applications in quality index prediction}, 
  year={early access, Oct. 2024, doi: 10.1109/TETCI.2024.3462486.},
  volume={},
  number={},
  pages={}}

@ARTICLE{ref31,
  author={Li, Yue and Liu, Lu and Feng, Gang},
  journal={IEEE Transactions on Systems, Man, and Cybernetics: Systems}, 
  title={Finite-time  $\mathcal{H}_{\infty}$  controller synthesis of T–S fuzzy systems}, 
  year={2020},
  volume={50},
  number={5},
  pages={1956-1963}}

@ARTICLE{refnew44,
  author={Mu, Yunfei and Zhang, Huaguang and Xi, Ruipeng and Gao, Zhiyun},
  journal={IEEE Transactions on Circuits and Systems II: Express Briefs}, 
  title={State and Fault Estimations for Discrete-Time T-S Fuzzy Systems With Sensor and Actuator Faults}, 
  year={2021},
  volume={68},
  number={10},
  pages={3326-3330}}

@ARTICLE{ref25,
  author={Gao, Zhiwei},
  journal={IEEE Transactions on Industrial Electronics}, 
  title={Fault Estimation and Fault-Tolerant Control for Discrete-Time Dynamic Systems}, 
  year={2015},
  volume={62},
  number={6},
  pages={3874-3884}}

@ARTICLE{ref26,
  author={Muramatsu, Hisayoshi and Katsura, Seiichiro},
  journal={IEEE Transactions on Industrial Informatics}, 
  title={An Adaptive Periodic-Disturbance Observer for Periodic-Disturbance Suppression}, 
  year={2018},
  volume={14},
  number={10},
  pages={4446-4456}}

@article{ref30,
author = {O. H. BOSGRA and A. J. J. VAN DER WEIDEN},
title = {Realizations in generalized state-space form for polynomial system matrices and the definitions of poles, zeros and decoupling zeros at infinity},
journal = {International Journal of Control},
volume = {33},
number = {3},
year = {1981},
pages = {393--411}}
  
@ARTICLE{Li_2020_TIE,
  author={Li, Yan and Fang, Hao and Chen, Jie},
  journal={IEEE Trans. Ind. Electron.}, 
  title={Anomaly detection and identification for multiagent systems subjected to physical faults and cyberattacks}, 
  year={Nov. 2020},
  volume={67},
  number={11},
  pages={9724-9733}}
  
@ARTICLE{Shiliang_2014_IJARS,
  author={Shao. Shiliang and Wang, Ting and Yao, Chen and Li, Xiaofan and Zhao Hai},
  journal={Int. J. Adv. Robot. Syst.}, 
  title={Distributed fault detection and isolation for flocking in a multi-robot system with imperfect communication}, 
  year={2014},
  volume={11},
  number={6},
  pages={86-93}}

@ARTICLE{Wang_2019_TII,
  author={Wang, Rui and Dong, Xiwang and Li, Qingdong and Ren, Zhang},
  journal={IEEE Trans. Ind. Inform.}, 
  title={Distributed time-varying formation control for multiagent systems with directed topology using an adaptive output-feedback approach}, 
  year={Aug. 2019},
  volume={15},
  number={8},
  pages={4676-4685}}
  
@ARTICLE{Zhu_2022_TCS1,
author={Zhu, Guoliang and Liu, Kexin and Gu, Haibo and Luo, Weilin and Lü, Jinhu},
  journal={IEEE Trans. Circuits Syst. I-Regul. Pap.}, 
  title={Observer-based event-triggered formation control of multi-agent systems with switching directed topologies}, 
  year={Mar. 2022},
  volume={69},
  number={3},
  pages={1323-1332}}

@ARTICLE{Masahiro_2020_TIE,
  author={Sato, Masahiro and Toda, Masayoshi},
  journal={IEEE Trans. Ind. Electron.}, 
  title={Adaptive Algorithms of Tuning and Switching Kalman and $ {H}_{\infty }$ Filters and Their Application to Estimation of Ship Oscillation With Time-Varying Frequencies}, 
  year={Jan. 2020},
  volume={67},
  number={1},
  pages={501-511}}
  
  %%%%%%%%%%%%%


@ARTICLE{Qiu_2021_ITSG,
  author={Qiu, Wei and Tang, Qiu and Zhu, Kunzhi and Wang, Weikang and Liu, Yilu and Yao, Wenxuan},
  journal={IEEE Trans. Smart Grid}, 
  title={Detection of synchrophasor false data injection attack using feature interactive network}, 
  year={Jan. 2021},
  volume={12},
  number={1},
  pages={659-670}}
  
@ARTICLE{Li_2020_TII,
  author={Li, XiaoJian and Shen, XinYu},
  journal={IEEE Trans. Ind. Inform.},
  title={A data-driven attack detection approach for DC servo motor systems based on mixed optimization strategy},
  year={Sept. 2020},
  volume={16},
  number={9},
  pages={5806-5813}}
  
@ARTICLE{Long_2022_TII,
  author={Chen, Long and Hu, Bin and Guan, ZhiHong},
  journal={IEEE Trans. Ind. Inform.},
  title={Adaptive event-triggered transmission scheduling in rate-limited multiloop remote control}, 
  year={Oct. 2022},
  volume={18},
  number={10},
  pages={6962-6972}}
  
@ARTICLE{Yong_2022_TCYB,
  author={Xu, Yong and Sun, Jian and Wu, ZhengGuang and Wang, Gang},
  journal={IEEE T. Cyber.}, 
  title={Fully distributed adaptive event-triggered control of networked systems with actuator bias faults}, 
  year={Oct. 2022},
  volume={52},
  number={10},
  pages={10773-10784}}
  
@ARTICLE{Shoaib_2022_TPS,
  author={Shoaib, Muhammad Asim and Khan, Abdul Qayyum and Mustafa, Ghulam and Gul, Sufi Tabbasum and Khan, Owais and Khan, Aadil Sarwar},
  journal={IEEE Trans. Power Syst.}, 
  title={A framework for observer-based robust fault detection in nonlinear systems With Application to Synchronous generators in power Systems}, 
  year={Mar. 2022},
  volume={37},
  number={2},
  pages={1044-1053}}
  
@article{Liang_2022_ISAT,
  title = {Multi-agent based event-triggered distributed cooperative fault detection},
  journal = {ISA Trans.},
  author = {Liang, Limei  and Liu, Shuai and Li, Yueyang and Zhong, Maiying},
  volume = {129},
  pages = {69-78},
  year = {Oct. 2022}}

@article{Hu_2022_JFI,
 title = {Zero-assignment and complex coefficient gain design of generalized proportional-integral observer for robust fault detection},
 author = {Hu, Yuxiang  and Dai, Xuewu and Cui, Dongliang and Jia, Zhian},
 journal = {J. Frankl. Inst.-Eng. Appl. Math.},
 volume = {359},
 number = {8},
 pages = {3831-3856},
 year = {2022}}

@ARTICLE{Yi_2019_TAC,
  author={Yi, Xinlei and Liu, Kun and Dimarogonas, Dimos V. and Johansson, Karl H.},
  journal={IEEE Trans. Autom. Control}, 
  title={Dynamic event-triggered and self-triggered control for multi-agent systems}, 
  year={Aug. 2019},
  volume={64},
  number={8},
  pages={3300-3307}}

@ARTICLE{Liang_TIM_2022,
  author={Liang, Limei and Liu, Shuai},
  journal={IEEE Trans. Instrum. Meas.}, 
  title={Event-triggered Distributed Attack Detection and Fault Diagnosis}, 
  year={early access, Oct. 25, 2022, doi:10.1109/TIM.2022.3216674},
  volume={},
  number={},
  pages={}}




@ARTICLE{Hisayoshi_2018_TII,
  author={Muramatsu, Hisayoshi and Katsura, Seiichiro},
  journal={IEEE Trans. Ind. Inform.}, 
  title={An adaptive periodic-disturbance observer for periodic-disturbance suppression}, 
  year={Oct. 2018},
  volume={14},
  number={10},
  pages={4446-4456}}

@ARTICLE{Li_2018_TIE,
  author={Li, Yan and Fang, Hao and Chen, Jie and Yu, Chengpu},
  journal={IEEE Trans. Ind. Electron.}, 
  title={Distributed cooperative fault detection for multiagent systems: A mixed ${H}_{\infty }/{H}_2$ optimization approach}, 
  year={Aug. 2018},
  volume={65},
  number={8},
  pages={6468-6477}}

@ARTICLE{Andras_2022_TIV,
  author={Palffy, Andras and Kooij, Julian F. P. and Gavrila, Dariu M.},
  journal={IEEE T. Intell. Veh.}, 
  title={Detecting darting out pedestrians with occlusion aware sensor fusion of radar and stereo camera}, 
  year={early access, Nov. 08, 2022, doi: 10.1109/TIV.2022.3220435.},
  volume={},
  number={},
  pages={}}

@ARTICLE{Zong_2022_IOT,
  author={Zong, Yan and Dai, Xuewu and Wei, Zhuangkun and Zou, Mengbang and Guo, Weisi and Gao, Zhiwei},
  journal={IEEE Internet Things J.}, 
  title={Robust time synchronisation for industrial internet of things by ${H}_{\infty}$ output feedback control}, 
  year={early access, Jan. 18, 2022, doi:10.1109/JIOT.2022.3144199},
  volume={},
  number={}}

@ARTICLE{Guo_2022_TVT,
  author={Guo, Ge and Zhao, Ziwei and Zhang, Renyongkang},
  journal={IEEE Trans. Veh. Technol.}, 
  title={Distributed trajectory optimization and fixed-time tracking control of a group of connected vehicles}, 
  year={early access, Oct. 10, 2022, doi:10.1109/TVT.2022.3212023},
  volume={},
  number={},
  pages={}}

@ARTICLE{Wang_2016_TII,
  author={Wang, YuLong and Han, QingLong},
  journal={IEEE Trans. Ind. Electron.}, 
  title={Network-based fault detection filter and controller coordinated design for unmanned surface vehicles in network environments}, 
  year={Oct. 2016},
  volume={12},
  number={5},
  pages={1753-1765}}

@ARTICLE{Li_2022_IEEE,
  author={Li, Fangyu and Xie, Rui and Yang, Bowen and Guo, Lulu and Ma, Ping and Shi, Jianjun and Ye, Jin and Song, WenZhan},
  journal={IEEE J. Emerg. Sel. Top. Power Electron.}, 
  title={Detection and identification of cyber and physical attacks on distribution power grids with PVs: An online high-dimensional data-driven approach}, 
  year={Feb. 2022},
  volume={10},
  number={1},
  pages={1282-1291}}

@ARTICLE{Lee_2022_IRAL,
  author={Lee, Suet and Milner, Emma and Hauert, Sabine},
  journal={IEEE Robot. Autom. Lett.}, 
  title={A data-driven method for metric extraction to detect faults in robot swarms}, 
  year={Oct. 2022},
  volume={7},
  number={4},
  pages={10746-10753}}

@ARTICLE{Barboni_2020_TAC,
  author={Barboni, Angelo and Rezaee, Hamed and Boem, Francesca and Parisini, Thomas},
  journal={IEEE Trans. Autom. Control}, 
  title={Detection of covert cyber-attacks in interconnected systems: A distributed model-based approach}, 
  year={Sept. 2020},
  volume={65},
  number={9},
  pages={3728-3741}}

@ARTICLE{Krishnan_2021_ICSL,
  author={Krishnan, Vishaal and Pasqualetti, Fabio},
  journal={IEEE Control Syst. Lett.}, 
  title={Data-driven attack detection for linear systems}, 
  year={April 2021},
  volume={5},
  number={2},
  pages={671-676}}

@ARTICLE{Teixeira_2015_ICSM,
  author={Teixeira, Andre and Sou, Kin Cheong and Sandberg, Henrik and Johansson, Karl Henrik},
  journal={IEEE Control Syst. Mag.}, 
  title={Secure control systems: A quantitative risk management approach}, 
  year={Feb. 2015},
  volume={35},
  number={1},
  pages={24-45}}

@ARTICLE{Horacio_2019_RE,
  author={Horacio, CoralEnriquez and John, CortesRomero and Sergio A., DoradoRojas},
  journal={Renew. Energy}, 
  title={Rejection of varying-frequency periodic load disturbances in wind-turbines through active disturbance rejection-based control}, 
  year={Oct. 2019},
  volume={141},
  number={},
  pages={217-235}}

@ARTICLE{Song_2020_ITPE,
  author={Song, Zhanfeng and Wang, Yaqi and Shi, Tingna},
  journal={IEEE Trans. Power Electron.}, 
  title={A dual-loop predictive control structure for permanent magnet synchronous machines with enhanced attenuation
 of periodic disturbances}, 
  year={Jan. 2020},
  volume={35},
  number={1},
  pages={760-774}}

@ARTICLE{Fei_2021_TFS,
  author={Fei, Zhongyang and Shi, Shuang and Ahn, Choon Ki and Basin, Michael V.},
  journal={IEEE Trans. Fuzzy Syst.}, 
  title={Finite-time control for switched T–S fuzzy systems via a dynamic event-triggered mechanism}, 
  year={Dec. 2021},
  volume={29},
  number={12},
  pages={3899-3909}}

@ARTICLE{new1,
  author={Shi, Yukun and Wang, Youqing},
  journal={IEEE Trans. Syst. Man Cybern. -Syst.}, 
  title={Online secure state estimation of multiagent systems using average consensus}, 
  year={2022},
  volume={52},
  number={5},
  pages={3174-3186}}

@ARTICLE{new2,
  author={Shi, Yukun and Wang, Youqing and Tuo, Jianyong},
  journal={IEEE-CAA J. Automatica Sin.}, 
  title={Distributed secure state estimation of multi-agent systems under homologous sensor attacks}, 
  year={2023},
  volume={10},
  number={1},
  pages={67-77}}

@ARTICLE{2022_IEEE_CSL,
  author={Zhang, Kangkang and Keliris, Christodoulos and Parisini, Thomas and Polycarpou, Marios M.},
  journal={IEEE Control Systems Letters}, 
  title={Identification of sensor replay attacks and physical faults for cyber-physical systems}, 
  year={2022},
  volume={6},
  number={},
  pages={1178-1183}}

@article{2021_IEEE_TCAS2,
  author    = {H. Guo and Z. Pang and J. Sun and J. Li},
  title     = {An output-coding-based detection scheme against replay attacks in cyber-physical systems},
  journal   = {IEEE Transactions on Circuits and Systems II: Express Briefs},
  volume    = {68},
  number    = {10},
  pages     = {3306--3310},
  year      = {2021},
  doi       = {10.1109/TCSII.2021.3063835}
}

@article{2023_ISA,
  author    = {M. Ramadan and F. Abdollahi},
  title     = {A passive isolation of sensor faults from un-stealthy attacks in uncertain nonlinear systems},
  journal   = {ISA Transactions},
  year      = {2023},
  doi       = {10.1016/j.isatra.2023.06.006}
}

@article{2017_IEEE_TNNLS,
  author    = {C. Keliris and M. Polycarpou and T. Parisini},
  title     = {An integrated learning and filtering approach for fault diagnosis of a class of nonlinear dynamical systems},
  journal   = {IEEE Transactions on Neural Networks and Learning Systems},
  volume    = {28},
  number    = {4},
  pages     = {988--1004},
  year      = {2017},
  doi       = {10.1109/TNNLS.2016.2579078}
}








